sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2022-03-17 doc/paper.Rmd
Note add_utm_columns()

An sdmTMB model requires a data frame that contains a response column, columns for any predictors, and columns for spatial coordinates.
It usually makes sense to convert the spatial coordinates to an equidistant projection such as the Universal Transverse Mercator (UTM) to ensure that distance remains constant throughout the study region [e.g., using `sf::st_transform()`, @pebesma2018].
<!-- TODO: Since this is not particular to your package, maybe the e.g. for how to do this should be moved to the appendix? I do explain the transformation for the owl data and added a sentence to the pcod appendix, but maybe still important to include here as well? -->
Here, we illustrate a spatial model fit to Pacific cod (*Gadus macrocephalus*) trawl survey data from Queen Charlotte Sound, British Columbia, Canada.
Our model contains a main effect of depth as a penalized smoother, a spatial random field, and Tweedie observation error.
Our data frame `pcod` (built into the package) has a column `year` for the year of the survey, `density` for biomass density of Pacific cod in the area swept for a given survey tow, `depth` for depth in meters of that tow, and spatial coordinates `X` and `Y`, which are UTM coordinates in kilometres.

>>>>

An sdmTMB model requires a data frame that contains a response column, columns for any predictors, and columns for spatial coordinates.
It usually makes sense to convert the spatial coordinates to an equidistant projection such as the Universal Transverse Mercator (UTM) to ensure that distance remains constant throughout the study region [e.g., using `sf::st_transform()`, @pebesma2018, or `sdmTMB::add_utm_columns()`].
<!-- TODO: Since this is not particular to your package, maybe the e.g. for how to do this should be moved to the appendix? I do explain the transformation for the owl data and added a sentence to the pcod appendix, but maybe still important to include here as well? -->
Here, we illustrate a spatial model fit to Pacific cod (*Gadus macrocephalus*) trawl survey data from Queen Charlotte Sound, British Columbia, Canada.
Our model contains a main effect of depth as a penalized smoother, a spatial random field, and Tweedie observation error.
Our data frame `pcod` (built into the package) has a column `year` for the year of the survey, `density` for biomass density of Pacific cod in the area swept for a given survey tow, `depth` for depth in meters of that tow, and spatial coordinates `X` and `Y`, which are UTM coordinates in kilometres.
